An Audio Interface for an Active Perception Navigation Aid for Blind People

### 2019-05-14 article.tex

\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{todonotes}
\usepackage[capitalise]{cleveref}

@@

%\begin{figure}
  %\centering
  %\begin{subfigure}[t]{0.45\textwidth}
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/tango_headphone.png}
  \caption{The Tango device and bone-conducting headset used by the participants. }\label{fig:tango-headphone}
\end{figure}
  %\end{subfigure}\hfill
  %\begin{subfigure}[t]{0.45\textwidth}
  %\end{subfigure}
  %\caption{The hardware used during the experiment, as well as a diagram showing the Tango device's coordinate system. }
%\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/camera_coordinate.pdf}
  \caption{A diagram showing the Tango's frame of reference and the target's pan ($\phi$) and tilt ($\theta$) angles.}\label{fig:cam-coords}
\end{figure}

@@

%The system is based on a concept proposed in~\cite{bellotto2013, lock2017portable}, which uses a Google Tango device.
This is an Android-based cellphone or tablet device that comes equipped with an RGB-D camera to sense colour and depth.
It combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
An added benefit of this platform is its familiar, compact form-factor which will help overcome the hurdle of user-acceptance and usability.

@@

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=50 120 80 50, width=0.4\textwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/pitch_gain_functions.png}
  \caption{The pitch gain functions for the 3 different gain settings. }\label{fig:pitch-gain}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.4\textwidth]{figures/err_lo.png}
  \caption{\emph{Lo} setting. }
  \label{fig:err-results-lo}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.4\textwidth]{figures/err_med.png}
  \caption{\emph{Med} setting. }
  \label{fig:err-results-med}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 60, width=0.4\textwidth]{figures/err_hi.png}
  \caption{\emph{Hi} setting. }
  \label{fig:err-results-hi}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=20 -70 100 100, width=0.4\textwidth]{figures/err_boxplot_medians.png}
  \caption{Error median.}
  \label{fig:err-boxplot-median}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=80 -70 100 0, width=0.4\textwidth]{figures/err_boxplot_std.png}
  \caption{Error standard deviations.}
  \label{fig:err-boxplot-std}
\end{figure}

\begin{table}
  \centering
  \caption{A table of the pan and tilt angular error results for the target search experiment. The results include the absolute average error ($\mu_{abs}$), average error ($\mu$) and standard deviations ($\sigma$) given in radians, as well as the Spearman ($R$) correlation scores.}
  \label{tab:results}
  \begin{tabular}{|c|l|c|c|c|c|}
    \hline
    \multicolumn{2}{|c|}{} & $\mu_{abs}$ & $\mu$ & $\sigma$ & $R$ \\\hline\hline
    & \emph{lo}  & 0.23 & -0.02 & 0.32 & 0.75 \\\cline{2-6}
    Pan & \emph{med} & 0.21 & -0.01 & 0.28 & 0.77 \\\cline{2-6}
    & \emph{hi}  & 0.22 & -0.05 & 0.31 & 0.75 \\\hline\hline
    & \emph{lo}  & 0.40 & -0.14 & 0.46 & 0.38 \\\cline{2-6}
    Tilt & \emph{med} & 0.32 & -0.12 & 0.36 & 0.48 \\\cline{2-6}
    & \emph{hi}  & 0.34 & -0.16 & 0.39 & 0.55 \\\hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \centering
  \caption{A table summarising the target search results of the participants with partial eyesight (P1 - P3). The results include the average error ($\mu$) and standard deviation ($\sigma$), given in radians in the pan and tilt dimensions.}
  \label{tab:vi-results}
  \begin{tabular}{|c|c|cc|cc|cc|}
    \hline
    \multicolumn{2}{|c|}{} & \multicolumn{2}{c|}{\emph{lo}} & \multicolumn{2}{c|}{\emph{med}} & \multicolumn{2}{c|}{\emph{hi}} \\
    \multicolumn{2}{|c|}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\hline\hline
    & P1 & 0.25 & 0.44 & 0.21 & 0.45 & 0.29 & 0.40 \\ \cline{2-8}
    Pan & P2 & 0.18 & 0.85 & 0.05 & 0.49 & -0.08 & 0.32 \\ \cline{2-8}
    & P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \hline\hline
    & P1 & -0.17 & 0.21 & -0.10 & 0.2 & -0.25 & 0.21 \\ \cline{2-8}
    Tilt & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\ \cline{2-8}
    & P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\ \hline
  \end{tabular}
\end{table}

>>>>

\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{todonotes}
\usepackage[capitalise]{cleveref}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}
  \caption{The Tango device and bone-conducting headset used by the participants. }\label{fig:tango-headphone}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\columnwidth]{figures/camera_coordinate.pdf}
  \caption{A diagram showing the Tango's frame of reference and the target's pan ($\phi$) and tilt ($\theta$) angles.}\label{fig:cam-coords}
\end{figure}

@@

\begin{anonsuppress}
The system is based on a concept proposed in~\cite{bellotto2013, lock2017portable}, which uses a Google Tango device.
\end{anonsuppress}
This is an Android-based cellphone or tablet device that comes equipped with an RGB-D camera to sense colour and depth.
It combines an inertial measurement unit with powerful and robust landmark recognition and image processing algorithms to localise itself in real-time.
An added benefit of this platform is its familiar, compact form-factor which will help overcome the hurdle of user-acceptance and usability.

@@

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=1.0\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\columnwidth]{figures/pitch_gain_functions.png}
  \caption{The pitch gain functions for the 3 different gain settings. }\label{fig:pitch-gain}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_lo.png}
  %\includegraphics[width=1.0\columnwidth]{figures/err_lo.png}
  \caption{\emph{Lo} setting. }\label{fig:err-results-lo}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_med.png}
  %\includegraphics[width=1.0\columnwidth]{figures/err_med.png}
  \caption{\emph{Med} setting. }\label{fig:err-results-med}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_hi.png}
  %\includegraphics[width=1.0\columnwidth]{figures/err_hi.png}
  \caption{\emph{Hi} setting. }\label{fig:err-results-hi}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=20 -70 100 100, width=0.8\columnwidth]{figures/err_boxplot_medians.png}
  \caption{Error median.}\label{fig:err-boxplot-median}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=80 -70 100 0, width=0.8\columnwidth]{figures/err_boxplot_std.png}
  \caption{Error standard deviations.}\label{fig:err-boxplot-std}
\end{figure}

\begin{table}
  \centering
  \caption{A table of the pan and tilt angular error results for the target search experiment. The results include the absolute average error ($\mu_{abs}$), average error ($\mu$) and standard deviations ($\sigma$) given in radians, as well as the Spearman ($R$) correlation scores.}\label{tab:results}
  \begin{tabular}{llcccc}
    \toprule
    \multicolumn{2}{c}{} & $\mu_{abs}$ & $\mu$ & $\sigma$ & $R$ \\\midrule
    & \emph{lo}  & 0.23 & -0.02 & 0.32 & 0.75 \\%\cmidrule{2-6}
    Pan & \emph{med} & 0.21 & -0.01 & 0.28 & 0.77 \\%\cmidrule{2-6}
    & \emph{hi}  & 0.22 & -0.05 & 0.31 & 0.75 \\\midrule
    & \emph{lo}  & 0.40 & -0.14 & 0.46 & 0.38 \\%\cmidrule{2-6}
    Tilt & \emph{med} & 0.32 & -0.12 & 0.36 & 0.48 \\%\cmidrule{2-6}
    & \emph{hi}  & 0.34 & -0.16 & 0.39 & 0.55 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}
  \centering
  \caption{A table summarising the target search results of the participants with partial eyesight (P1 - P3). The results include the average error ($\mu$) and standard deviation ($\sigma$), given in radians in the pan and tilt dimensions.}\label{tab:vi-results}
  \begin{tabular}{llcccccc}
    \toprule
    \multicolumn{2}{c}{} & \multicolumn{2}{c}{\emph{lo}} & \multicolumn{2}{c}{\emph{med}} & \multicolumn{2}{c}{\emph{hi}} \\
    \multicolumn{2}{c}{} & $\mu_l$ & $\sigma_l$ & $\mu_m$ & $\sigma_m$ & $\mu_h$ & $\sigma_h$ \\\midrule
         & P1 &  0.25 & 0.44 &  0.21 & 0.45 &  0.29 & 0.40 \\% \cline{2-8}
    Pan  & P2 &  0.18 & 0.85 &  0.05 & 0.49 & -0.08 & 0.32 \\% \cline{2-8}
         & P3 & -0.10 & 0.67 & -0.08 & 0.61 & -0.08 & 0.50 \\ \midrule
         & P1 & -0.17 & 0.21 & -0.10 & 0.2  & -0.25 & 0.21 \\% \cline{2-8}
    Tilt & P2 & -0.87 & 0.26 & -0.05 & 0.21 & -0.15 & 0.18 \\% \cline{2-8}
         & P3 & -0.57 & 0.31 & -0.57 & 0.45 & -0.38 & 0.39 \\% \hline
    \bottomrule
  \end{tabular}
\end{table}
